---
title: "Report"
format: docx
execute: 
  echo: false
  warning: false
  message: false
params:
  village: "Ijumangabo A"
---

```{r}
library(tidyverse)
village_selected <-  params$village
```


# `r village_selected` village report

`r today()`

```{r}
data <-  read_csv(file ="./data/Kakumiro_House_to_House_registeration_2024_07_29_16_54_06_830093.csv",name_repair = "universal_quiet", na = "n/a" ) 
```

```{r}

data_cleaned <- data |> 
  unite("section2.q4_village", `section2.q4_village1`:`section2.q4_village2`, na.rm = TRUE) |> 
  mutate(section2.q3_parish = str_to_title(section2.q3_parish ), 
         section2.q4_village = str_to_title(section2.q4_village)) |> 
  filter(section2.q4_village  == village_selected)


data_filtered <- data_cleaned |> 
  filter(section4.Q15_do == "yes")

number_of_households <- data_cleaned |>  
  group_by(section2.q4_village, section4.q12_hh_number) |> 
  count() |> ungroup() |> 
  count(section2.q4_village) |> pull(n)
```


There are `r length(data_filtered$section2.q3_parish)` children in `r village_selected` village in our eligible category (4 to 59 months) whose care givers were interviewed. 

We reached `r number_of_households` households 


```{r}
#data_filtered |>  
#  count(section2.q4_village) |> 
#  ggplot(aes(x = fct_reorder(`section2.q4_village`, n), y = n) ) +
#  geom_col() +
 # coord_flip() +
#  geom_label(aes(label = n ))
```

## Number of Zero Dose children per village

```{r}

## Said No; i.e they didn't vaccinate
zd_said_no <- data_filtered |> 
  filter(`section6.q26_past` == "no")
```

```{r}
## Said Yes; i.e they vaccinated but withno card and didn't mention the thighs as part

zd_said_yes_card_no_thigh_no <- data_filtered |> 
  filter(`section6.q26_past` == "yes" & `section6.q28_card` == "no" & ask.q31.thigh == FALSE)
```

```{r}

## Said Yes; i.e they vaccinated, they have a card but don't have DPT1, DPT2, DPT3
zd_said_yes_card_yes_dpts_no <- data_filtered |> 
  filter(`section6.q26_past` == "yes") |>  
  filter(q28_infor.q28_dpt1 != "yes") |> 
  filter(q28_infor.q28_dpt2 != "yes") |> 
  filter(q28_infor.q28_dpt3 != "yes")
```

```{r}
data_zd <- bind_rows(zd_said_no, zd_said_yes_card_no_thigh_no, zd_said_yes_card_yes_dpts_no) |> count(section2.q4_village) |> pull(n)

```
There are `r data_zd` Zero dose children in `r village_selected` village 



```{r}
# zd_geospatial <- data_zd |> select(section2.q3_parish, section2.q4_village, section2.q6_gps, section2._q6_gps_latitude, section2._q6_gps_longitude, section4.q12_hh_number, section4.q13_holdhead, section4.q14_contact, sectionfive.q16_care,sectionfive.q17_tel, sectionfive.q18_common, would.q21_child, would.q22_sex, would.q24_age_in_months, would.q25_place,would.other1) |>
#   rename("parish" = section2.q3_parish, "village" = section2.q4_village, "gps" = section2.q6_gps, "lat" = section2._q6_gps_latitude, "lon" = section2._q6_gps_longitude,"HHnum" = section4.q12_hh_number, "HHhead" = section4.q13_holdhead, "HHtel" = section4.q14_contact, "caregivers_name" = sectionfive.q16_care,"caregivers_tel" = sectionfive.q17_tel, "caregivers_common" = sectionfive.q18_common, "childs_name" = would.q21_child, "childs_sex" = would.q22_sex, "childs_age" = would.q24_age_in_months, "place_of_birth" = would.q25_place, "place_of_birth_other" = would.other1)

#write_csv(zd_geospatial, "./data/geospatial-data.csv")
```

```{r}
#flextable(zd_geospatial)
```

# How about underimmunised children?

```{r}
change_to_number <- function(x){
  ifelse(x == "yes", 1, 0)}

data_with_cards <- data_filtered |>
    filter(section6.q28_card == "yes") 


number_with_cards <- nrow(data_with_cards)
```

To determine under-immunized children, we shall only focus on `r number_with_cards` children who had  `child health cards`  


```{r}
data_with_cards |> 
  select(q28_infor.q28_bcg:q28_infor.q28_mr2) |> 
  mutate(across(q28_infor.q28_bcg:q28_infor.q28_mr2, change_to_number)) |> 
  summarise(across(q28_infor.q28_bcg:q28_infor.q28_mr2, sum, na.rm = T)) |> 
  pivot_longer(q28_infor.q28_bcg:q28_infor.q28_mr2,names_to = "antigen",  values_to = "doses_given")|>
  mutate(antigen  = str_remove(antigen, "q28_infor.q28_")) |> 
  filter(antigen %in% c("bcg","dpt1", "dpt3", "mr1", "mr2" )) |> 
  mutate(antigen  = str_to_upper(antigen), 
         percent_doses_given = round(doses_given/ number_with_cards, 3)*100) |> 
  ggplot(aes(x = antigen, y = percent_doses_given)) +
  geom_col() +
  ylim(c(0, 120))+
  geom_label(aes(label = glue::glue("{percent_doses_given}% \n{doses_given} "))) +
   labs(
    y = "Percentage of children vaccinated", 
    x = "Antigen")

```


## Reasons for Zero dose and under-immunised


```{r}
data_reasons1 <- data_filtered |> 
  filter(section6.q26_past == "no") |> 
  select(section6.q32_3.Religious_beliefs:section6.q32_3.too_many_vaccine_injections) |> 
  summarise(across(section6.q32_3.Religious_beliefs:section6.q32_3.too_many_vaccine_injections, sum, na.rm = T)) |> pivot_longer(section6.q32_3.Religious_beliefs:section6.q32_3.too_many_vaccine_injections,names_to = "reasons",  values_to = "total") |> mutate(reasons  = str_remove(reasons, "section6.q32_3.")) |> arrange(desc(total))
  

data_reasons2 <- data_filtered |> 
  filter(q28_infor.q28 == "no") |> 
  select(q28_infor.q32_2.Religious_beliefs:q28_infor.q32_2.too_many_vaccine_injections) |> 
 summarise(across(q28_infor.q32_2.Religious_beliefs:q28_infor.q32_2.too_many_vaccine_injections, sum, na.rm = T)) |> pivot_longer(q28_infor.q32_2.Religious_beliefs:q28_infor.q32_2.too_many_vaccine_injections,names_to = "reasons",  values_to = "total") |> mutate(reasons  = str_remove(reasons, "q28_infor.q32_2.")) |> arrange(desc(total))


data_reasons3 <- data_filtered |> 
   filter(section6.q28_card == "no") |> 
  select(ask.q32.Religious_beliefs:ask.q32.too_many_vaccine_injections) |> 
  summarise(across(ask.q32.Religious_beliefs:ask.q32.too_many_vaccine_injections, sum, na.rm = T)) |>     pivot_longer(ask.q32.Religious_beliefs:ask.q32.too_many_vaccine_injections, names_to = "reasons",  values_to = "total") |> mutate(reasons  = str_remove(reasons, "ask.q32.")) |> arrange(desc(total))

bind_rows(data_reasons1,data_reasons2, data_reasons3) |> 
  group_by(reasons) |> 
  summarise(total = sum(total)) |> 
  mutate(reasons = str_replace_all(reasons, "_", " "), 
         reasons = str_replace_all(reasons, "\\.", " "),
         reasons = str_to_sentence(reasons), 
         reasons = str_wrap(reasons, width = 35)) |> 
  top_n(10, total) |> 
  ggplot(aes(x = fct_reorder(reasons, total), y = total)) +
  geom_col() +
  geom_label(aes(label =  total))+
  coord_flip() +
    labs(
    x = "Reasons", 
    y = "Number of times mentioned")


```

## How many Zero dose and under-immunised have been vaccinated during the H2H registeration (Saturady to Tuesday)

**(If not what are reasons for those who have not yet vaccinated)**

## Recommendations

## Action plan

