---
title: "Report"
format: docx
execute: 
  echo: false
  warning: false
  message: false
---

```{r}

setwd("C:/Users/Gk Coordinator/Desktop/r-projects/kakumiro-village-reports/reports/activity-summary-report/")
library(UBOSpopulation)
library(UNEPItargets)
library(tidyverse)
library(scales)
library(showtext)
library(svglite)
library(ggrepel)


font_add_google("Roboto", family = "Roboto")


font_add_google("Lora", family = "Lora")


font_add_google("Roboto Mono", "Roboto Mono")

showtext_auto()

grey_lighter <- "#dee0e3"
grey_light <- "#888A8C"
grey_dark <- "#939598"
blue_dark <- "#144673"
red_dark <- "#852922"
green_dark <- "#097061"

theme_stroytelling_bar <- function(){ 
  theme_classic()+
  theme(axis.text = element_text(family = "Roboto Mono", size = 12, colour = "#888A8C"),
            axis.ticks = element_line(colour = grey_light),
            axis.title = element_text(family = "Roboto",  size = 15, colour = grey_light),
            axis.line = element_line(colour = grey_light),
            plot.caption = element_text(family = "Roboto",  size = 11, colour = grey_light),
            legend.text = element_text(colour = grey_light),
            legend.title = element_text(colour = grey_light, face = "bold"),
            legend.position = "none",
            plot.subtitle =  element_text(family = "Roboto",  size = 20, colour = grey_light),
            plot.title  = element_text(family = "Roboto",  size = 30, colour = "#585859"))
}

```


# Ijumangabo and Kyakuterekera Zero Dose activity summary report

`r today()`

```{r}
data <-  read_csv(file ="./data/Kakumiro_House_to_House_registeration_2024_08_07_05_53_10_309929.csv",name_repair = "universal_quiet", na = "n/a" ) 
```

```{r}
data_cleaned <- data |> 
  unite("section2.q4_village", `section2.q4_village1`:`section2.q4_village2`, na.rm = TRUE) |> 
  mutate(section2.q3_parish = str_to_title(section2.q3_parish ), 
         section2.q4_village = str_to_title(section2.q4_village))

data_filtered <- data_cleaned|> 
  filter(section4.Q15_do == "yes") |>
   mutate(age = interval(would.q23_was_born, dmy("31-07-2024")) %/% months(1), 
          age = case_when(!between(age, 4, 59) ~ would.q24_age_in_months,
                          .default = age)) |>
  filter(between(age, 4, 59) )

number_of_households <-  data_cleaned |>  
  group_by(section2.q4_village, section4.q12_hh_number) |> 
  count() |> ungroup() |> 
  count(section2.q4_village) |> pull(n) |> sum()
  
```

There are `r length(data_filtered$section2.q3_parish)` children in our eligible category (4 to 59 months) whose care givers were interviewed   

We reached `r number_of_households` households 

## Number of House holds per village

```{r}
data_cleaned |>  
  group_by(section2.q4_village, section4.q12_hh_number) |> 
  count() |> ungroup() |> 
  count(section2.q4_village) |> 
  ggplot(aes(x = fct_reorder(`section2.q4_village`, n), y = n) ) +
  geom_col(fill = grey_dark) +
  coord_flip() +
  geom_label(aes(label = n )) +
  labs(
    y = "Number of House holds", 
    x = "Villages") +
  theme_stroytelling_bar()

#ggsave(filename = "Number of HH per village.svg", device = "svg", width = 36, height = 18, units = "cm" ) 
```
## Mwitanzige and District performance for the last 3 year

```{r}
district_sc_data <- read_csv("data/Kakumiro and Mwitanzige SC- DPT1 and MR2 FY2324-2.csv")|>
  mutate(month = my(month))
```

### DPT1 coverage

```{r}
  ggplot() +
  geom_line(data = district_sc_data, mapping = aes(x = month, y = DPT1, colour = orgunit), linewidth = 1, lineend = "round") +
  geom_hline(yintercept = c(100), linetype = "dashed", color = grey_light )+
  geom_point(data = district_sc_data |> filter(month == dmy("01062024")),
             aes(x= month, y = DPT1, colour = orgunit)) +
  geom_text(data =district_sc_data |> filter(orgunit == "Mwitanzige Subcounty" & DPT1 < 100), 
            mapping = aes(x= month , y = DPT1, label = glue::glue("{DPT1}%"), colour = orgunit),
            nudge_y = - 5, size = 5, family = "Roboto Mono") +
    geom_text(data =district_sc_data |> filter(orgunit == "Mwitanzige Subcounty" & DPT1 > 150), 
            mapping = aes(x= month , y = DPT1, label = glue::glue("{DPT1}%"), colour = orgunit),
            nudge_y = 5, size = 5, family = "Roboto Mono")+
  theme_classic() +
  scale_color_manual(values = c("Mwitanzige Subcounty" = blue_dark,
                                 "Kakumiro District" = grey_dark)) + 
    scale_x_date(date_breaks = "2 months",date_labels = "%b%y",
                 limits = c(dmy("01012022"), dmy("01072024")))+
    scale_y_continuous(labels = scales::percent_format(scale = 1,accuracy = 1), limits = c(0, NA) ) +
    labs(x = "Period",
         y = "DPT1 Coverage",
         caption = "Data source: DHIS2 07/08/2024",
         title = NULL,
         subtitle = NULL) +
theme_stroytelling_bar()
  
#ggsave(filename = "DPT1-coverage.svg", device = "svg", width = 36, height = 18, units = "cm" )  

```

## MR 1 Coverage

```{r}

  ggplot() +
    geom_line(data = district_sc_data, mapping = aes(x = month, y = MR1, colour = orgunit), linewidth = 1, lineend = "round") +
    geom_hline(yintercept = c(100), linetype = "dashed", color = grey_light )+
    geom_point(data = district_sc_data |> filter(month == dmy("01062024")),
               aes(x= month, y = MR1, colour = orgunit)) +
   geom_text(data =district_sc_data |> filter(orgunit == "Mwitanzige Subcounty" & MR1 < 100), 
            mapping = aes(x= month , y = MR1, label = glue::glue("{MR1}%"), colour = orgunit), size = 5, nudge_y = -15, family = "Roboto Mono") +
    geom_text_repel(data =district_sc_data |> filter(orgunit == "Mwitanzige Subcounty" & MR1 > 250), 
            mapping = aes(x= month , y = MR1, label = glue::glue("{MR1}%"), colour = orgunit), size = 5, nudge_y = 15, family = "Roboto Mono")+
    theme_classic() +
    scale_color_manual(values = c("Mwitanzige Subcounty" = blue_dark,
                                  "Kakumiro District" = grey_dark)) + 
    scale_x_date(date_breaks = "2 months",date_labels = "%b%y",
                 limits = c(dmy("01012022"), dmy("01072024")))+
    scale_y_continuous(labels = scales::percent_format(scale = 1,accuracy = 1, big.mark = ","), limits = c(0, 1500) ) +
    labs(x = "Period",
         y = "MR1 Coverage",
         caption = "Data source: DHIS2 07/08/2024",
         title = NULL,
         subtitle = NULL) +
  theme_stroytelling_bar()
  
 # ggsave(filename = "MR1-coverage.svg", device = "svg", width = 36, height = 18, units = "cm" ) 
```

## MR 2 Coverage

```{r}

  ggplot() +
    geom_line(data = district_sc_data, mapping = aes(x = month, y = MR2, colour = orgunit), linewidth = 1, lineend = "round") +
    geom_hline(yintercept = c(100), linetype = "dashed", color = grey_light )+
    geom_point(data = district_sc_data |> filter(month %in% dmy(c("01062024", "01082022", "01102022"))),
               aes(x= month, y = MR2, colour = orgunit)) +
   geom_text(data =district_sc_data |> filter(orgunit == "Mwitanzige Subcounty" & MR2 < 100), 
            mapping = aes(x= month , y = MR2, label = glue::glue("{MR2}%"), colour = orgunit), size = 5, nudge_y = -15, family = "Roboto Mono") +
    geom_text_repel(data =district_sc_data |> filter(orgunit == "Mwitanzige Subcounty" & MR2 > 250), 
            mapping = aes(x= month , y = MR2, label = glue::glue("{MR2}%"), colour = orgunit), size = 5, nudge_y = 15, family = "Roboto Mono")+
    theme_classic() +
    scale_color_manual(values = c("Mwitanzige Subcounty" = blue_dark,
                                  "Kakumiro District" = grey_dark)) + 
    scale_x_date(date_breaks = "2 months",date_labels = "%b%y",
                 limits = c(dmy("01012022"), dmy("01072024")))+
    scale_y_continuous(labels = scales::percent_format(scale = 1,accuracy = 1, big.mark = ","), limits = c(0, 1500) ) +
    labs(x = "Period",
         y = "MR2 Coverage",
         caption = "Data source: DHIS2 07/08/2024",
         title = NULL,
         subtitle = NULL) +
  theme_stroytelling_bar()
  
#ggsave(filename = "MR2-coverage.svg", device = "svg", width = 36, height = 18, units = "cm" ) 
```


## Number of Zero Dose children per village

```{r}

## Said No; i.e they didn't vaccinate
zd_said_no <- data_filtered |> 
  filter(`section6.q26_past` == "no")

## Said Yes; i.e they vaccinated but withno card and didn't mention the thighs as part

zd_said_yes_card_no_thigh_no <- data_filtered |> 
  filter(`section6.q26_past` == "yes" & `section6.q28_card` == "no" & ask.q31.thigh == FALSE)


zd_said_no_cards <- data_filtered |>
    filter(section6.q28_card == "no") 

## Said Yes; i.e they vaccinated, they have a card but don't have DPT1, DPT2, DPT3
zd_said_yes_card_yes_dpts_no <- data_filtered |> 
  filter(`section6.q26_past` == "yes") |>  
  filter(q28_infor.q28_dpt1 != "yes") |> 
  filter(q28_infor.q28_dpt2 != "yes") |> 
  filter(q28_infor.q28_dpt3 != "yes")
#data_zd_indvidual <- bind_rows(zd_said_no, zd_said_yes_card_no_thigh_no, zd_said_yes_card_yes_dpts_no) 

data_zd_indvidual <- bind_rows(zd_said_no, zd_said_no_cards, zd_said_yes_card_yes_dpts_no) 


data_zd <- data_zd_indvidual |> 
  group_by(section2.q3_parish, section2.q4_village ) |> 
  count() |> 
  ungroup()
```

There are `r sum(data_zd$n)` Zero dose children in identified 

```{r}

  ggplot(data = data_zd, mapping = aes(x = fct_reorder(`section2.q4_village`, n), y = n, fill = `section2.q3_parish`) ) +
  geom_col() +
  scale_fill_manual(values = c("Kyakuterekera" = red_dark,
                                "Ijumangabo" = grey_lighter)) + 
  coord_flip() +
  geom_label(data = data_zd |> filter(section2.q3_parish == "Kyakuterekera"), 
             mapping = aes(label = n ), size = 4, family = "Roboto Mono", color = "white") +
    geom_label(data = data_zd |> filter(section2.q3_parish == "Ijumangabo"), 
             mapping = aes(label = n ), size = 4, family = "Roboto Mono", color = "black") +
    labs(
    y = "Number of Zero Dose children", 
    x = "Villages") +
    theme_stroytelling_bar()

   #ggsave(filename = "ZD by village.svg", device = "svg", width = 36, height = 18, units = "cm" )
```
## Analysis of the Zero Dose children

```{r}
zd_geospatial <- data_zd_indvidual |> select(section2.q3_parish, section2.q4_village, section2.q6_gps, section2._q6_gps_latitude, section2._q6_gps_longitude, section4.q12_hh_number, section4.q13_holdhead, section4.q14_contact, sectionfive.q16_care,sectionfive.q17_tel, sectionfive.q18_common, would.q21_child, would.q22_sex, would.q24_age_in_months,would.q23_was_born, would.q25_place,would.other1) |>
    rename("parish" = section2.q3_parish, "village" = section2.q4_village, "gps" = section2.q6_gps, "lat" = section2._q6_gps_latitude, "lon" = section2._q6_gps_longitude,"HHnum" = section4.q12_hh_number, "HHhead" = section4.q13_holdhead, "HHtel" = section4.q14_contact, "caregivers_name" = sectionfive.q16_care,"caregivers_tel" = sectionfive.q17_tel, "caregivers_common" = sectionfive.q18_common, "childs_name" = would.q21_child, "childs_sex" = would.q22_sex, "childs_age" = would.q24_age_in_months,"childs_DOB" = would.q23_was_born, "place_of_birth" = would.q25_place, "place_of_birth_other" = would.other1)
# 
# 
# write_csv(zd_geospatial, "./data/geospatial-data.csv")
```



```{r}
## Zero dose of Mwitanzige subcounty for the Last 5 years
subcounty_zd_before <- read_csv("data/ZD in mwitanzige 2021 - 2024.csv") |> 
    mutate(period = factor(period)) |> 
    filter(orgunit == "Mwitanzige Subcounty")

#### ZD children found
  
   
 zd_children_cleaned <-   zd_geospatial |> 
     select(- c(gps,  lat,   lon, HHhead , HHtel, caregivers_name ,caregivers_tel ,caregivers_common)) |> 
     mutate(YOB = as.factor(year(childs_DOB)),
       age = interval(childs_DOB, dmy("31-07-2024")) %/% months(1)) |>
     filter(age >= 4) |> 
     select(-c(HHnum, childs_name, childs_age, childs_DOB))
 
zd_data_by_year <-  zd_children_cleaned |> 
   count(YOB, name = "ZD_identified") |> 
   left_join( subcounty_zd_before, by = c("YOB" = "period")) 

   ggplot()+
   geom_col(data = zd_data_by_year, aes(x = YOB, y = ZD), fill = grey_lighter) +
   geom_col(data = zd_data_by_year, aes(x = YOB, y = ZD_identified), fill = blue_dark)+
   geom_label(data =zd_data_by_year, mapping = aes(x= YOB , y = ZD, label = ZD), size = 4, family = "Roboto Mono", color = grey_light) +
     geom_label(data =zd_data_by_year, mapping = aes(x= YOB , y = ZD_identified, label = ZD_identified), size = 4, family = "Roboto Mono", color = blue_dark) +
   theme_classic() +
   geom_hline(yintercept = 0, linetype = "solid", color = "black" )+
   scale_fill_manual(values = c("pos" = red_dark,
                                "neg" = grey_dark)) + 
   scale_y_continuous( limits = c(-200, 100) ) +
   labs(x = "Year",
        y = "Number of ZD",
        caption = "Data source: DHIS2 & H2H registeration 07/08/2024",
        title = NULL,
        subtitle = NULL) +
   theme(axis.text = element_text(family = "Roboto Mono", size = 12, colour = "#888A8C"),
         axis.ticks = element_line(colour = grey_light),
         axis.title = element_text(family = "Roboto",  size = 15, colour = grey_light),
         axis.line = element_line(colour = grey_light),
         plot.caption = element_text(family = "Roboto",  size = 11, colour = grey_light),
         legend.text = element_text(colour = grey_light),
         legend.title = element_text(colour = grey_light, face = "bold"),
         legend.position = "none",
         plot.subtitle =  element_text(family = "Roboto",  size = 20, colour = grey_light),
         plot.title  = element_text(family = "Roboto",  size = 30, colour = "#585859"))
   
 #  ggsave(filename = "ZD by year- Mwitanzige.svg", device = "svg", width = 36, height = 18, units = "cm" ) 
   
```
## Zero dose by Place of Birth

```{r}

zd_by_place_birth <- zd_children_cleaned |> 
  mutate(place_of_birth = 
           case_when(place_of_birth == "other" ~ place_of_birth_other,.default = place_of_birth)) |> 
 select(-place_of_birth_other) |> 
 count(place_of_birth) |> 
 mutate(place_of_birth = str_to_title(place_of_birth),
        place_of_birth = case_when(str_detect(place_of_birth, "Home") ~ "Home", 
                                   is.na(place_of_birth) ~ "Don't Know",
                                   .default = place_of_birth )) |> 
  group_by(place_of_birth) |> 
  summarise(n = sum(n)) |> 
  mutate(status = case_when(place_of_birth %in% c("Traditional Birth Attendants", "Home") ~ "pos", 
                                   .default = "neg"),
         place_of_birth = str_wrap(place_of_birth, width = 10, whitespace_only = F, exdent = 0))



 ggplot() +
 geom_col(data = zd_by_place_birth , aes(x = reorder(place_of_birth, desc(n)), y = n, fill =status)) +
 geom_label(data =zd_by_place_birth , mapping = aes(x = place_of_birth, y = n, label = n), size = 5, family = "Roboto Mono", color = grey_dark) +
 theme_classic() +
 scale_fill_manual(values = c("pos" = red_dark,
                              "neg" = grey_lighter)) + 
 scale_y_continuous( limits = c(0, 200) ) +
 
 labs(x = "Place of Birth",
      y = "Number of ZD",
      caption = "Data source: H2H registeration 07/08/2024",
      title = NULL,
      subtitle = NULL) +
theme_stroytelling_bar()
     
   #  ggsave(filename = "ZD by Place of Birth- Mwitanzige.svg", device = "svg", width = 36, height = 18, units = "cm" )     
     
```


# How about underimmunised children?

```{r}
change_to_number <- function(x){case_when(x == "yes" ~ 0, x == "no" ~ 1, is.na(x) ~ 1)}


data_card_cleaned <- data_filtered |>
  mutate(section6.q28_card = case_when(is.na(section6.q28_card) ~ "no", 
                                       .default = section6.q28_card))
data_with_cards <- data_card_cleaned |> 
                    filter(section6.q28_card == "yes") 

data_with_cards_no <-  data_card_cleaned  |>
    filter(section6.q28_card == "no")


number_with_cards <- nrow(data_with_cards)
```

To determine under-immunized children, we shall only focus on `r number_with_cards` children who had  `child health cards`  


```{r}
underimmunised_by_antigen_long <- data_card_cleaned |> 
  select(c(section2.q3_parish, section2.q4_village, section2.q6_gps, section2._q6_gps_latitude, section2._q6_gps_longitude, section4.q12_hh_number, section4.q13_holdhead, section4.q14_contact, sectionfive.q16_care,sectionfive.q17_tel, sectionfive.q18_common, would.q21_child, would.q22_sex, would.q25_place,would.other1), c(q28_infor.q28_bcg:q28_infor.q28_mr2 ), age ) |>
    rename("parish" = section2.q3_parish, "village" = section2.q4_village, "gps" = section2.q6_gps, "lat" = section2._q6_gps_latitude, "lon" = section2._q6_gps_longitude,"HHnum" = section4.q12_hh_number, "HHhead" = section4.q13_holdhead, "HHtel" = section4.q14_contact, "caregivers_name" = sectionfive.q16_care,"caregivers_tel" = sectionfive.q17_tel, "caregivers_common" = sectionfive.q18_common, "childs_name" = would.q21_child, "childs_sex" = would.q22_sex, "place_of_birth" = would.q25_place, "place_of_birth_other" = would.other1)
```





```{r}
underimmunised_by_antigen_long_clean <- underimmunised_by_antigen_long |> 
  select(c(c(q28_infor.q28_bcg:q28_infor.q28_mr2), age )) |> 
  mutate(age_cat = case_when(age >= 18 ~ "elig_MR2",
                             age >= 9 ~ "elig_MR1",
                             age >= 4 ~ "elig_BCG_DPT")) |> 
  select(-age) 

### Some children were record to be 

children_with_cards_df <- underimmunised_by_antigen_long_clean|> 
  count(age_cat) 
 
```


```{r}
change_to_number <- function(x){case_when(x == "yes" ~ T, x == "no" ~ F, is.na(x) ~ F)}

## Eligible to BCG to DPT1 
underimmunised_by_antigen_long_clean2 <- underimmunised_by_antigen_long_clean |>
   mutate(across(q28_infor.q28_bcg:q28_infor.q28_mr2, change_to_number)) |> 
  group_by(age_cat) |>
  summarise(across(q28_infor.q28_bcg:q28_infor.q28_mr2, sum)) |>
pivot_longer(q28_infor.q28_bcg:q28_infor.q28_mr2,names_to = "antigen",  values_to = "immunised")|>
  mutate(antigen  = str_remove(antigen, "q28_infor.q28_"))
  
underimmunised_by_antigen_elig_bcg_dpts <- underimmunised_by_antigen_long_clean2 |> 
  filter(antigen %in% c("bcg","dpt1", "dpt3" )) |> 
  group_by(antigen) |> 
  summarise(immunised = sum(immunised))|> 
  mutate(children_with_cards = children_with_cards_df |> pull(n) |> sum())

underimmunised_by_antigen_elig_mr1 <- underimmunised_by_antigen_long_clean2 |> 
  filter(antigen %in% c("mr1") & age_cat %in% c( "elig_MR1","elig_MR2"  )) |> 
  group_by(antigen) |> 
  summarise(immunised = sum(immunised)) |> 
  mutate(children_with_cards = children_with_cards_df |> 
           filter(age_cat %in% c("elig_MR1","elig_MR2" )) |> pull(n) |> sum())

underimmunised_by_antigen_elig_mr2 <- underimmunised_by_antigen_long_clean2 |> 
  filter(antigen %in% c("mr2") & age_cat %in% c("elig_MR2" )) |> 
  group_by(antigen) |> 
  summarise(immunised = sum(immunised)) |> 
 mutate(children_with_cards = children_with_cards_df |> 
           filter(age_cat %in% c("elig_MR2" )) |> pull(n) |> sum())


underimmunised_by_antigen_data_plot <-  bind_rows(underimmunised_by_antigen_elig_bcg_dpts, underimmunised_by_antigen_elig_mr1, underimmunised_by_antigen_elig_mr2)|> 
  mutate(antigen  = str_to_upper(antigen), 
         underimmunised = children_with_cards - immunised, 
         percent_underimmunised = round((underimmunised/children_with_cards)*100, 2))
```


```{r}
    ggplot()+
      geom_col(data = underimmunised_by_antigen_data_plot, aes(x = antigen, y = children_with_cards),
               fill = grey_lighter) +
      geom_col(data = underimmunised_by_antigen_data_plot, aes(x = antigen, y = underimmunised), fill = red_dark)+
      geom_label(data = underimmunised_by_antigen_data_plot, mapping = aes(x= antigen , y = children_with_cards, label = children_with_cards), size = 3.5 , family = "Roboto Mono", color = grey_light) +
      geom_label(data = underimmunised_by_antigen_data_plot,
                 mapping = aes(x= antigen , y = underimmunised, 
                               label = glue::glue("{underimmunised}\n{percent_underimmunised}%")), 
                               size = 3.5, family = "Roboto Mono", color = red_dark) +
      scale_y_continuous( limits = c(0, 1200) ) +
      labs(x = "Antigen",
           y = "Number of doses",
           caption = "Data source: H2H registeration 31/07/2024",
           title = NULL,
           subtitle = NULL)+
  theme_stroytelling_bar()
     
    
   # ggsave(filename = "unimmunised by antigen.svg", device = "svg", width = 36, height = 18, units = "cm" ) 
    
```

```{r}
immunised_children <- read_csv("./data/vaccinated children by antigen.csv")

immunised_by_antigen_data_plot <- underimmunised_by_antigen_data_plot |> left_join(immunised_children) |> 
  select(-percent_underimmunised) |> 
   mutate(percent_immunised = round((doses_given/underimmunised)*100, 2))
  
 ggplot()+
      geom_col(data = immunised_by_antigen_data_plot, aes(x = antigen, y = children_with_cards),
               fill = grey_lighter) +
      geom_col(data = immunised_by_antigen_data_plot, aes(x = antigen, y = underimmunised), fill = red_dark)+
      geom_col(data = immunised_by_antigen_data_plot, aes(x = antigen, y = doses_given), fill = green_dark)+
      geom_label(data = immunised_by_antigen_data_plot, mapping = aes(x= antigen , y = children_with_cards, label = children_with_cards), size = 3.5 , family = "Roboto Mono", color = grey_light) +
      geom_label(data = immunised_by_antigen_data_plot, mapping = aes(x= antigen , y = underimmunised, label = underimmunised), size = 3.5 , family = "Roboto Mono", color = red_dark) +
      geom_label(data = immunised_by_antigen_data_plot,
                 mapping = aes(x= antigen , y = doses_given, 
                               label = glue::glue("{doses_given}\n{percent_immunised}%")), 
                               size = 3.5, family = "Roboto Mono", color = green_dark) +
      scale_y_continuous( limits = c(0, 1200) ) +
      labs(x = "Antigen",
           y = "Number of doses",
           caption = "Data source: H2H registeration 31/07/2024",
           title = NULL,
           subtitle = NULL)+
  theme_stroytelling_bar()

 #ggsave(filename = "immunised by antigen.svg", device = "svg", width = 36, height = 18, units = "cm" ) 
```


## Reasons for Zero dose and under-immunised


```{r}
data_reasons1 <- data_filtered |> 
 # filter(section6.q26_past == "no") |> 
  select(section6.q32_3.Religious_beliefs:section6.q32_3.too_many_vaccine_injections) |> 
  summarise(across(section6.q32_3.Religious_beliefs:section6.q32_3.too_many_vaccine_injections, sum, na.rm = T)) |> pivot_longer(section6.q32_3.Religious_beliefs:section6.q32_3.too_many_vaccine_injections,names_to = "reasons",  values_to = "total") |> mutate(reasons  = str_remove(reasons, "section6.q32_3.")) |> arrange(desc(total))
  

data_reasons2 <- data_filtered |> 
  #filter(q28_infor.q28 == "no") |> 
  select(q28_infor.q32_2.Religious_beliefs:q28_infor.q32_2.too_many_vaccine_injections) |> 
 summarise(across(q28_infor.q32_2.Religious_beliefs:q28_infor.q32_2.too_many_vaccine_injections, sum, na.rm = T)) |> pivot_longer(q28_infor.q32_2.Religious_beliefs:q28_infor.q32_2.too_many_vaccine_injections,names_to = "reasons",  values_to = "total") |> mutate(reasons  = str_remove(reasons, "q28_infor.q32_2.")) |> arrange(desc(total))


data_reasons3 <- data_filtered |> 
  # filter(section6.q28_card == "no") |> 
  select(ask.q32.Religious_beliefs:ask.q32.too_many_vaccine_injections) |> 
  summarise(across(ask.q32.Religious_beliefs:ask.q32.too_many_vaccine_injections, sum, na.rm = T)) |>     pivot_longer(ask.q32.Religious_beliefs:ask.q32.too_many_vaccine_injections, names_to = "reasons",  values_to = "total") |> mutate(reasons  = str_remove(reasons, "ask.q32.")) |> arrange(desc(total))

 reasons_plot_data <- bind_rows(data_reasons1,data_reasons2, data_reasons3) |> 
  group_by(reasons) |> 
  summarise(total = sum(total)) |> 
  mutate(reasons = str_replace_all(reasons, "_", " "), 
         reasons = str_replace_all(reasons, "\\.", " "),
         reasons = str_to_sentence(reasons), 
         reasons = str_wrap(reasons, width = 35, whitespace_only = F, exdent = 0)) |> 
  mutate(reasons = fct_lump(reasons, n = 9, w = total, other_level = "Other reasons")) |> 
   group_by(reasons) |> 
  summarise(total = sum(total)) |> 
   mutate(status = case_when(total >= 40 ~ "top",.default = "low"))
  
  

  ggplot(data  = reasons_plot_data, aes(x = fct_reorder(reasons, total), y = total, fill = status) ) +
  geom_col() +
   scale_fill_manual(values = c("top" = red_dark,
                                "low" = grey_lighter))+
  geom_label( data = reasons_plot_data |> filter(status == "top"),aes(label =  total), color = "white")+
  geom_label( data = reasons_plot_data |> filter(status == "low"),aes(label =  total), color = "black")+
  coord_flip() +
    labs(
    x = "Reasons", 
    y = "Number of times mentioned", 
    caption = "Data source: H2H registeration 31/07/2024") +
  theme_classic() +
      theme(axis.text = element_text(family = "Roboto Mono", size = 11, colour = "#888A8C"),
            axis.ticks = element_line(colour = grey_light),
            axis.title = element_text(family = "Roboto",  size = 15, colour = grey_light),
            axis.line = element_line(colour = grey_light),
            plot.caption = element_text(family = "Roboto",  size = 11, colour = grey_light),
            legend.text = element_text(colour = grey_light),
            legend.title = element_text(colour = grey_light, face = "bold"),
            legend.position = "none",
            plot.subtitle =  element_text(family = "Roboto",  size = 20, colour = grey_light),
            plot.title  = element_text(family = "Roboto",  size = 30, colour = "#585859"))
  
  #ggsave(filename = "reasons for not vaccinating children.svg", device = "svg", width = 36, height = 18, units = "cm" ) 
```



## How many Zero dose and under-immunised have been vaccinated during the H2H registeration (Saturady to Tuesday)

**(If not what are reasons for those who have not yet vaccinated)**

## Recommendations

## Action plan


