---
title: "Report"
format: docx
execute: 
  echo: false
  warning: false
  message: false
---

```{r}
library(tidyverse)
```


# Ijumangabo and Kyakuterekera Zero Dose activity summary report

`r today()`

```{r}
data <-  read_csv(file ="./data/Kakumiro_House_to_House_registeration_2024_08_07_05_53_10_309929.csv",name_repair = "universal_quiet", na = "n/a" ) 
```

```{r}
data_cleaned <- data |> 
  unite("section2.q4_village", `section2.q4_village1`:`section2.q4_village2`, na.rm = TRUE) |> 
  mutate(section2.q3_parish = str_to_title(section2.q3_parish ), 
         section2.q4_village = str_to_title(section2.q4_village))

data_filtered <- data_cleaned|> 
  filter(section4.Q15_do == "yes")

number_of_households <- 
  
```

There are `r length(data_filtered$section2.q3_parish)` children in our eligible category (4 to 59 months) whose care givers were interviewed   

We reached `r number_of_households` households 

## Number of House holds per village

```{r}
data_cleaned |>  
  group_by(section2.q4_village, section4.q12_hh_number) |> 
  count() |> ungroup() |> 
  count(section2.q4_village) |> 
  ggplot(aes(x = fct_reorder(`section2.q4_village`, n), y = n) ) +
  geom_col() +
  coord_flip() +
  geom_label(aes(label = n )) +
  labs(
    y = "Number of House holds", 
    x = "Villages")
```

```{r}
#data_filtered |>  
#  count(section2.q4_village) |> 
#  ggplot(aes(x = fct_reorder(`section2.q4_village`, n), y = n) ) +
#  geom_col() +
 # coord_flip() +
#  geom_label(aes(label = n ))
```

## Number of Zero Dose children per village

```{r}

## Said No; i.e they didn't vaccinate
zd_said_no <- data_filtered |> 
  filter(`section6.q26_past` == "no")
```

```{r}
## Said Yes; i.e they vaccinated but withno card and didn't mention the thighs as part

zd_said_yes_card_no_thigh_no <- data_filtered |> 
  filter(`section6.q26_past` == "yes" & `section6.q28_card` == "no" & ask.q31.thigh == FALSE)
```

```{r}

## Said Yes; i.e they vaccinated, they have a card but don't have DPT1, DPT2, DPT3
zd_said_yes_card_yes_dpts_no <- data_filtered |> 
  filter(`section6.q26_past` == "yes") |>  
  filter(q28_infor.q28_dpt1 != "yes") |> 
  filter(q28_infor.q28_dpt2 != "yes") |> 
  filter(q28_infor.q28_dpt3 != "yes")
```

```{r}
data_zd_indvidual <- bind_rows(zd_said_no, zd_said_yes_card_no_thigh_no, zd_said_yes_card_yes_dpts_no) 


data_zd <- data_zd_indvidual |> 
  count(section2.q4_village) 
```

There are `r sum(data_zd$n)` Zero dose children in identified 

```{r}
data_zd |> 
  ggplot(aes(x = fct_reorder(`section2.q4_village`, n), y = n) ) +
  geom_col() +
  coord_flip() +
  geom_label(aes(label = n )) +
    labs(
    y = "Number of Zero Dose children", 
    x = "Villages"
  )
```

```{r}
  zd_geospatial <- data_zd_indvidual |> select(section2.q3_parish, section2.q4_village, section2.q6_gps, section2._q6_gps_latitude, section2._q6_gps_longitude, section4.q12_hh_number, section4.q13_holdhead, section4.q14_contact, sectionfive.q16_care,sectionfive.q17_tel, sectionfive.q18_common, would.q21_child, would.q22_sex, would.q24_age_in_months,would.q23_was_born, would.q25_place,would.other1) |>
    rename("parish" = section2.q3_parish, "village" = section2.q4_village, "gps" = section2.q6_gps, "lat" = section2._q6_gps_latitude, "lon" = section2._q6_gps_longitude,"HHnum" = section4.q12_hh_number, "HHhead" = section4.q13_holdhead, "HHtel" = section4.q14_contact, "caregivers_name" = sectionfive.q16_care,"caregivers_tel" = sectionfive.q17_tel, "caregivers_common" = sectionfive.q18_common, "childs_name" = would.q21_child, "childs_sex" = would.q22_sex, "childs_age" = would.q24_age_in_months,"childs_DOB" = would.q23_was_born, "place_of_birth" = would.q25_place, "place_of_birth_other" = would.other1)
# 
# 
# write_csv(zd_geospatial, "./data/geospatial-data.csv")
```

```{r}
#flextable(zd_geospatial)
```

# How about underimmunised children?

```{r}
change_to_number <- function(x){case_when(x == "yes" ~ 0, x == "no" ~ 1, is.na(x) ~ 1)}

data_with_cards <- data_filtered |>
    filter(section6.q28_card == "yes") 


number_with_cards <- nrow(data_with_cards)
```

To determine under-immunized children, we shall only focus on `r number_with_cards` children who had  `child health cards`  


```{r}
underimmunised_by_antigen_long <- data_with_cards |> 
  select(c(section2.q3_parish, section2.q4_village, section2.q6_gps, section2._q6_gps_latitude, section2._q6_gps_longitude, section4.q12_hh_number, section4.q13_holdhead, section4.q14_contact, sectionfive.q16_care,sectionfive.q17_tel, sectionfive.q18_common, would.q21_child, would.q22_sex, would.q24_age_in_months,would.q23_was_born, would.q25_place,would.other1), c(q28_infor.q28_bcg:q28_infor.q28_mr2 )) |>
    rename("parish" = section2.q3_parish, "village" = section2.q4_village, "gps" = section2.q6_gps, "lat" = section2._q6_gps_latitude, "lon" = section2._q6_gps_longitude,"HHnum" = section4.q12_hh_number, "HHhead" = section4.q13_holdhead, "HHtel" = section4.q14_contact, "caregivers_name" = sectionfive.q16_care,"caregivers_tel" = sectionfive.q17_tel, "caregivers_common" = sectionfive.q18_common, "childs_name" = would.q21_child, "childs_sex" = would.q22_sex, "childs_age" = would.q24_age_in_months,"childs_DOB" = would.q23_was_born, "place_of_birth" = would.q25_place, "place_of_birth_other" = would.other1)
```





```{r}
underimmunised_by_antigen_long_clean <- underimmunised_by_antigen_long |> 
  select(c(c(q28_infor.q28_bcg:q28_infor.q28_mr2),
           childs_age, childs_DOB )) |> 
  mutate(age = interval(childs_DOB, dmy("31-07-2024")) %/% months(1), 
         childs_age = case_when(is.na(childs_age)~ age, 
                                .default = childs_age)) |> 
  
  filter(childs_age > 3.9) |> 
  mutate(age_cat = case_when(childs_age >= 18 ~ "elig_MR2",
                             childs_age >= 9 ~ "elig_MR1",
                             childs_age >= 4 ~ "elig_BCG_DPT")) |> 
  select(-c( childs_DOB,age, childs_age)) 

### Some children were record to be 

children_with_cards <- underimmunised_by_antigen_long_clean|> 
  count(age_cat)
 
```


```{r}
change_to_number <- function(x){case_when(x == "yes" ~ T, x == "no" ~ F, is.na(x) ~ F)}

## Eligible to BCG to DPT1 
underimmunised_by_antigen_long_clean |>
   mutate(across(q28_infor.q28_bcg:q28_infor.q28_mr2, change_to_number)) |> 
  group_by(age_cat) |> 
  summarise(across(q28_infor.q28_bcg:q28_infor.q28_mr2, sum)) |> 
pivot_longer(q28_infor.q28_bcg:q28_infor.q28_mr2,names_to = "antigen",  values_to = "immunised")|>
  mutate(antigen  = str_remove(antigen, "q28_infor.q28_")) |> 
  filter(antigen %in% c("bcg","dpt1", "dpt3", "mr1", "mr2" )) |> 
  
  mutate(antigen  = str_to_upper(antigen), 
         number_with_cards = case_when(antigen == "BCG" ~ 740,
                                       antigen == "DPT1" ~ 740,
                                       antigen == "DPT3" ~ 740,
                                       antigen == "MR1" ~ 657,
                                       antigen == "MR2" ~ 537), 
         underimmunised = number_with_cards - immunised ) 
         percent_underimmunised = round((underimmunised/number_with_cards)*100, 2))
```


```{r}
write_csv(underimmunised_by_antigen, "./data/underimmunised_by_antigen.csv")


underimmunised_by_antigen |> 
  ggplot(aes(x = antigen, y = underimmunised)) +
  geom_col() +
  ylim(c(0, 800))+
  geom_label(aes(label =  underimmunised)) +
   labs(
    y = "number of underimmunised", 
    x = "Antigen")

```


## Reasons for Zero dose and under-immunised


```{r}
data_reasons1 <- data_filtered |> 
  filter(section6.q26_past == "no") |> 
  select(section6.q32_3.Religious_beliefs:section6.q32_3.too_many_vaccine_injections) |> 
  summarise(across(section6.q32_3.Religious_beliefs:section6.q32_3.too_many_vaccine_injections, sum, na.rm = T)) |> pivot_longer(section6.q32_3.Religious_beliefs:section6.q32_3.too_many_vaccine_injections,names_to = "reasons",  values_to = "total") |> mutate(reasons  = str_remove(reasons, "section6.q32_3.")) |> arrange(desc(total))
  

data_reasons2 <- data_filtered |> 
  filter(q28_infor.q28 == "no") |> 
  select(q28_infor.q32_2.Religious_beliefs:q28_infor.q32_2.too_many_vaccine_injections) |> 
 summarise(across(q28_infor.q32_2.Religious_beliefs:q28_infor.q32_2.too_many_vaccine_injections, sum, na.rm = T)) |> pivot_longer(q28_infor.q32_2.Religious_beliefs:q28_infor.q32_2.too_many_vaccine_injections,names_to = "reasons",  values_to = "total") |> mutate(reasons  = str_remove(reasons, "q28_infor.q32_2.")) |> arrange(desc(total))


data_reasons3 <- data_filtered |> 
   filter(section6.q28_card == "no") |> 
  select(ask.q32.Religious_beliefs:ask.q32.too_many_vaccine_injections) |> 
  summarise(across(ask.q32.Religious_beliefs:ask.q32.too_many_vaccine_injections, sum, na.rm = T)) |>     pivot_longer(ask.q32.Religious_beliefs:ask.q32.too_many_vaccine_injections, names_to = "reasons",  values_to = "total") |> mutate(reasons  = str_remove(reasons, "ask.q32.")) |> arrange(desc(total))

bind_rows(data_reasons1,data_reasons2, data_reasons3) |> 
  group_by(reasons) |> 
  summarise(total = sum(total)) |> 
  mutate(reasons = str_replace_all(reasons, "_", " "), 
         reasons = str_replace_all(reasons, "\\.", " "),
         reasons = str_to_sentence(reasons), 
         reasons = str_wrap(reasons, width = 35)) |> 
  top_n(10, total) |> 
  ggplot(aes(x = fct_reorder(reasons, total), y = total)) +
  geom_col() +
  geom_label(aes(label =  total))+
  coord_flip() +
    labs(
    x = "Reasons", 
    y = "Number of times mentioned")


```
## How many Zero dose and under-immunised have been vaccinated during the H2H registeration (Saturady to Tuesday)

**(If not what are reasons for those who have not yet vaccinated)**

## Recommendations

## Action plan


